PART A: PRIMARY ANALYSIS!
READING DATA IN R
1.
```{r}
setwd("c:/Users/vaibhav/Desktop/DataSets")
data.df<-read.csv("MbaStartingSalariesData.csv")
View(data.df)
```
SUMMARY OF DATA
2(a)
```{r}
summary(data.df)
```
2(b)
```{r}
library(psych)
describe(data.df)
```
REMOVING PEOPLE WHO DIDN'T ANSWER SURVEY
3(a)
```{r}
newdata.df<-data.df[which(data.df$salary!=998),]
View(newdata.df)
dim(newdata.df)
```
3(b)SUMMARIZING THE NEW DATA SET
```{r}
summary(newdata.df)
```
3(c)Finding % unplaced
```{r}
table1<-with(newdata.df,table(newdata.df$salary))
prop.table(table1)*100
```
->Hence out of total people who did give the survey 39.47% were not placed and remainf 60.53% were placed
FINDING THE FACTORS OF WHY ONE WAS NOT PLACED OR PLACED BY COMPAIRING THE AVERAGES OF ALL
4.
```{r}
placed.df<-newdata.df[which(newdata.df$salary!=0),]
View(placed.df)
unplaced.df<-newdata.df[which(newdata.df$salary==0),]
View(unplaced.df)
```
COMPARING PLACED AND UNPLACED STUDENTS DATA
5(a) UNPLACED
```{r}
table2<-with(unplaced.df,table(unplaced.df$sex))
table2
prop.table(table2)*100
table4<-with(unplaced.df,table(unplaced.df$satis))
table4
```
```{r}
mean.age.unplaced<-mean(unplaced.df$age)
mean.gmat_tot.unplaced<-mean(unplaced.df$gmat_tot)
mean.gmat_qpc.unplaced<-mean(unplaced.df$gmat_qpc)
mean.gmat_vpc.unplaced<-mean(unplaced.df$gmat_vpc)
mean.gmat_tpc.unplaced<-mean(unplaced.df$gmat_tpc)
mean.s_avg.unplaced<-mean(unplaced.df$s_avg)
mean.f_avg.unplaced<-mean(unplaced.df$f_avg)
mean.work_yrs.unplaced<-mean(unplaced.df$work_yrs)
```
5(b) PLACED
```{r}
table5<-with(placed.df,table(placed.df$sex))
table5
prop.table(table5)*100
table7<-with(placed.df,table(placed.df$satis))
table7
```
```{r}
mean.age.placed<-mean(placed.df$age)
mean.gmat_tot.placed<-mean(placed.df$gmat_tot)
mean.gmat_qpc.placed<-mean(placed.df$gmat_qpc)
mean.gmat_vpc.placed<-mean(placed.df$gmat_vpc)
mean.gmat_tpc.placed<-mean(placed.df$gmat_tpc)
mean.s_avg.placed<-mean(placed.df$s_avg)
mean.f_avg.placed<-mean(placed.df$f_avg)
mean.work_yrs.placed<-mean(placed.df$work_yrs)
```
5(C)
```{r}
mean.age.DIFF<-mean(placed.df$age)-mean(unplaced.df$age)
mean.gmat_tot.DIFF<-mean(placed.df$gmat_tot)-mean(unplaced.df$gmat_tot)
mean.gmat_qpc.DIFF<-mean(placed.df$gmat_qpc)-mean(unplaced.df$gmat_qpc)
mean.gmat_vpc.DIFF<-mean(placed.df$gmat_vpc)-mean(unplaced.df$gmat_vpc)
mean.gmat_tpc.DIFF<-mean(placed.df$gmat_tpc)-mean(unplaced.df$gmat_tpc)
mean.s_avg.DIFF<-mean(placed.df$s_avg)-mean(unplaced.df$s_avg)
mean.f_avg.DIFF<-mean(placed.df$f_avg)-mean(unplaced.df$f_avg)
mean.work_yrs.DIFF<-mean(placed.df$work_yrs)-mean(unplaced.df$work_yrs)
```
```{r}
mean.age.DIFF
mean.gmat_tot.DIFF
mean.gmat_qpc.DIFF
mean.gmat_vpc.DIFF
mean.gmat_tpc.DIFF
mean.s_avg.DIFF
mean.f_avg.DIFF
mean.work_yrs.DIFF
```


EXECUTIVE SUMMARY 1: General Understanding
1.Age
Age of unplaced people is higher than that of placed people by almost 1.5 years
Hence in general people with lesser age did get placed
2.Sex
  Placed:Out of all placed 74% are male rest are female
  Unplaced:Out of all unplaced ~74% are male rest are female
  Hence Sex is not an issue as overall number of males are high, number of placed and unplaced males are high too
3.gmat_tot: GMAT total score
The difference in GMAT score of placed and unplaced people is 4.94.
Hence people who scored more on an average did get placed.
4.gmat_qpc: Quantitative GMAT percentile
The difference in quantitative GMAT percentile of placed and unplaced people is 2.19.
Hence people who have higher Percentile did get placed.
5.gmat_vpc:Verbal GMAT percentile
The difference in verbal GMAT percentile of placed and unplaced people is 0.359.
Hence people who have higher verbalPercentile did get placed.
6.gmat_tpc: overall Gmat percentile
The difference in overall GMAT percentile of placed and unplaced people is 2.18
Hence people who have higherPercentile did get placed.
7.s_avg: Spring MBA Average
People who are unplaced SUPRISINGLY had higher Spring average
8.f_avg: Fall MBA Average
People who are unplaced SUPRISINGLY had higher Fall average
9.Working Years
People who are unplaced SUPRISINGLY had more working experience too.
10. Satisfaction
People who were unplaced were moe satisfied infact no. one rated below 4.

PART B COMPARISION BETWEEN PLACED AND UNPLACED
```{r}
newdata.df$sex[newdata.df$sex==1]='Male'
newdata.df$sex[newdata.df$sex==2]='Female'
newdata.df$frstlang[newdata.df$frstlang== 1]='English'
newdata.df$frstlang[newdata.df$frstlang== 2]='Other'
newdata.df$GotPlaced = (newdata.df$salary >1000)
newdata.df$GotPlaced <- factor(newdata.df$GotPlaced)
View(newdata.df)
```
```{r}
table8<-with(newdata.df,table(newdata.df$GotPlaced))
table8
```

125 got placed 103 didnot
```{r}
placed.df$sex[placed.df$sex==1]='Male'
placed.df$sex[placed.df$sex==2]='Female'
placed.df$frstlang[placed.df$frstlang== 1]='English'
placed.df$frstlang[placed.df$frstlang== 2]='Other'
table9<-with(placed.df,table(placed.df$sex))
table9
table10<-with(placed.df,table(placed.df$frstlang))
table10
table14<-table(placed.df$sex,placed.df$frstlang)
table14
```

102 Males got placed whereas 36 females
122 people who were placed knew English 16 didnt
```{r}
unplaced.df$sex[unplaced.df$sex==1]='Male'
unplaced.df$sex[unplaced.df$sex==2]='Female'
unplaced.df$frstlang[unplaced.df$frstlang== 1]='English'
unplaced.df$frstlang[unplaced.df$frstlang== 2]='Other'
table11<-with(unplaced.df,table(unplaced.df$sex))
table11
table12<-with(unplaced.df,table(unplaced.df$frstlang))
table12
table13<-table(unplaced.df$sex,unplaced.df$frstlang)
table13
```
67 Males were unplaced 23 females were placed
82 knew English 8 did not
PART C:VISUALIZATION
Visualizing Salary vs Various factors
```{r}
par(mfrow=c(2,2))
boxplot(salary~age,data=data.df,main="Salary vs age",horizontal=TRUE)
boxplot(salary~sex,data=data.df,main="Salary vs sex",horizontal=TRUE)
boxplot(salary~frstlang,data=data.df,main="Salary vs Language",horizontal=TRUE)
boxplot(salary~satis,data=data.df,main="Salary vs Satisfaction",horizontal=TRUE)
```

PART D: REGRESSION
Dependent Variable: Salary
Independent Variable: age,sex,gmat_tot,gmat_qpc,gmat_vpc,gmat_tpc,s_avg,s_favg,quarter,work_yrs,firstlang,satis

Model1: Seeing how MBA factors like s_avg, f_avg,quarter affect salary
```{r}
fit1<-lm(placed.df$salary~placed.df$gmat_tot+placed.df$gmat_qpc+placed.df$gmat_vpc+placed.df$work_yrs)
summary(fit1)
```



