```{r}
setwd("C:/Users/vaibhav/Desktop/DataSets")
Store24.df<-read.csv("Store24.csv")
attach(Store24.df)
View(Store24.df)
```
Use R to measure the mean and standard deviation of Profit.
```{r}
mean(Profit)
sd(Profit)
```
Use R to measure the mean and standard deviation of MTenure.
```{r}
mean(MTenure)
sd(MTenure)
```
Use R to measure the mean and standard deviation of CTenure.
```{r}
mean(CTenure)
sd(CTenure)
```
Use R to print the {StoreID, Sales, Profit, MTenure, CTenure} of the top 10 most profitable stores.
```{r}
attach(Store24.df)
newdata<-Store24.df[order(-Store24.df$Profit),]
newdata[1:10,1:5]
```
Use R to print the {StoreID, Sales, Profit, MTenure, CTenure} of the bottom 10 least profitable stores.
```{r}
attach(Store24.df)
newdata<-Store24.df[order(Store24.df$Profit),]
newdata[1:10,1:5]
```
Use R to draw a scatter plot of Profit vs. MTenure.
```{r}
library(car)
scatterplot(y=Profit,x=MTenure,main="Profit vs. MTenure",col="black",smoother.args=list(ity=2))
abline(lm(Store24.df$Profit~Store24.df$MTenure),col="red",lty="dotted")
```
Use R to draw a scatter plot of Profit vs. CTenure.
```{r}
plot(y=Profit,x=CTenure,main="Profit vs. CTenure",col="black")
abline(lm(Store24.df$Profit~Store24.df$CTenure),col="red",lty="dotted")
```
Use R to construct a Correlation Matrix for all the variables in the dataset. (Display the numbers up to 2 Decimal places)
```{r}
round(cor(Store24.df),2)
```
Use R to measure the correlation between Profit and MTenure. (Display the numbers up to 2 Decimal places)
```{r}
round(cor(Store24.df$Profit,Store24.df$MTenure),2)
```
Use R to measure the correlation between Profit and CTenure.  (Display the numbers up to 2 Decimal places)
```{r}
round(cor(Store24.df$Profit,Store24.df$CTenure),2)
```
Use R to construct the following Corrgram based on all variables in the dataset
```{r}
library(corrgram)
corrgram(Store24.df,order=TRUE,lower.panel=panel.shade,upper.panel=panel.pie,text.panel=panel.txt,main="Corrgram of Store24")
```
Run a Pearson's Correlation test on the correlation between Profit and MTenure. What is the p-value?
```{r}
cor.test(Store24.df$Profit,Store24.df$MTenure)
```
Run a Pearson's Correlation test on the correlation between Profit and CTenure. What is the p-value?
```{r}
cor.test(Store24.df$Profit,Store24.df$CTenure)
```
Run a regression of Profit on {MTenure, CTenure Comp, Pop, PedCount, Res, Hours24, Visibility}.
```{r}

fit<-lm(Profit~MTenure+CTenure+Comp+Pop+PedCount+Res+Hours24+Visibility,Store24.df)
summary(fit)
```
List the explanatory variable(s) whose beta-coefficients are statistically significant (p < 0.05).

Mtenure, Comp,PedCount

List the explanatory variable(s) whose beta-coefficients are not statistically significant (p > 0.05).

Visibility

What is expected change in the Profit at a store, if the Manager's tenure i.e. number of months of experience with Store24, increases by one month?

760.993$

What is expected change in the Profit at a store, if the Crew's tenure i.e. number of months of experience with Store24, increases by one month?

944.978


Executive Summary
1)Effect of Tenure of managers and crew on profits was observed. It was found that tenure of managers in top 10 shops was 4 times 10 least profitable store
2)Pearson's Correlation test proves that p value is 8.193e-05 for MTenure and  0.02562 for CTenure. Hence Mtenure is strongly correlated to profits . Hence Managers affect the profit at a store more.
3)Corrgram shows visual correlation between all variables and hence makes understanding simple
4) Regression Ananlysis shows that M tenure ie tenure of manager, Number of competitors per 10,000 people within a1/2 mile radius and Population in that radius affect Profit more .
It had predicted  model using which we can predict profit of any store.""

